XXXXX

### 2014-09-30 paper/paper1.tex
R-200-NEGATIVE-LITERAL-CONSTRAINTS

\begin{ex}
<Jedi> {
    :feelingForce (true) ,
    :attitute ('good') ,
    :laserSwordColor ('blue') ,
    :numberLaserSwords ('1'^^xsd:nonNegativeInteger) }
<Sith> {
    :feelingForce (true) ,
    :attitute (!'good') ,
    :laserSwordColor (!'blue') ,
    :numberLaserSwords ('2'^^xsd:nonNegativeInteger) }
\end{ex}

@@

\begin{ex}
:Joda 
    :feelingForce (true) ;
    :attitute ('good') ;
    :laserSwordColor ('blue') ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger .
\end{ex}

@@

\begin{ex}
:DarthSidious
    :feelingForce (true) ;
    :attitute ('evil') ;
    :laserSwordColor ('red') ,
    :numberLaserSwords '2'^^xsd:nonNegativeInteger . 
\end{ex}

@@

>>>>

\url{http://w3.org/brief/Mzk2}

\begin{ex}
<Jedi> {
    :feelingForce (true) ,
    :attitute ('good') ,
    :laserSwordColor ('blue') ,
    :numberLaserSwords ('1'^^xsd:nonNegativeInteger) }
<Sith> {
    :feelingForce (true) ,
   !:attitute ('good') ,
   !:laserSwordColor ('blue') ,
    :numberLaserSwords ('2'^^xsd:nonNegativeInteger) }
\end{ex}

@@

\begin{ex}
:Joda 
    :feelingForce true ;
    :attitute 'good' ;
    :laserSwordColor 'blue' ;
    :numberLaserSwords '1'^^xsd:nonNegativeInteger .
\end{ex}

@@

\begin{ex}
:DarthSidious
    :feelingForce true ;
    :attitute 'evil' ;
    :laserSwordColor 'red' ;
    :numberLaserSwords '2'^^xsd:nonNegativeInteger . 
\end{ex}

@@

\url{http://w3.org/brief/Mzk0}
